---
title: "Sample LPP"
author: "ArcadisGen"
date: "2022-08-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem

A store has requested a manufacturer to produce pants and sports jackets.

For materials, the manufacturer has 750 m ^2 of cotton textile and 1000 m^2 of polyester. Every pair of trousers (1 unit) needs 1 m^2 of cotton and 2 m ^2 of polyester. Every jacket needs 1.5 m ^2 of cotton and 1 m^2 of polyester. The price of the trousers is fixed at £50 and the jacket, £40. What is the number of trousers and jackets that the manufacturer must give to the stores so that these items obtain a maximum sale?

## Solution

### Step 1 - Define Decision Variables

+---------------+---------------+
| Item          | Variable      |
+===============+===============+
| Trousers      |       x       |
|               |               |
+---------------+---------------+
| Jackets       |       y       |
|               |               |
+---------------+---------------+

### Step 2 - Constraints


| Material   |  Trousers  |  Jackets  | Available Quantity |
|------------|:----------:|----------:|-------------------:|
| Cotton     |    1       | 1.5       | 750                |
| Polyester  |    2       | 1         | 1000               |

1) Cotton Constraint    - 1 * x + 1.5 * y <= 750
2) Polyester Constraint - 2 * x + 1 * y   <= 1000
3) x, y should be integers

### Step 3 - Objective Function

Price of the Trousers is £50 and the jacket, £40

Maximize - 50 * x + 40 * y

### Code

```{r, echo = TRUE}
# Load lpSolve
library(lpSolve)

## Set the coefficients of the decision variables -> Objective Function C
C <- c(50, 40)

## Constraint Matrix
### LHS of Constraints
A <- matrix(c(1, 1.5,
              2, 1), nrow=2, byrow=TRUE)

## Equality of Constraints

eq <- c("<=", 
        "<=")

### RHS of constraints
B <- c(750,
       1000)


# Find the optimal solution
optimum <-  lp(direction="max",
               objective.in = C,
               const.mat = A,
               const.dir = eq,
               const.rhs = B,
               all.int = T)

# Print status: 0 = success, 2 = no feasible solution
print(optimum$status)

best_sol <- optimum$solution
names(best_sol) <- c("Trousers", "Jackets")
print(best_sol)

# Check the value of objective function at optimal point
print(paste("Total Revenue: ", optimum$objval, sep=""))

```